
\documentclass{article}
\usepackage[margin=1in]{geometry} % set the margins
\usepackage{graphicx} % package for including images
\usepackage{fancyhdr} % package for fancy header and footer
% all paragraphs should not be indented
\setlength\parindent{0pt}
% set the spacing between paragraphs
\setlength{\parskip}{1em}
\pagestyle{fancy}
\fancyhf{} % clear header/footer
\renewcommand{\headrulewidth}{0pt} % remove horizontal line in header

\begin{document}

\noindent Dear Hiring Manager,


I am a Lead Machine Learning Engineer eager to leverage my extensive experience in model development and deployment to contribute to Rocket Money's mission of enhancing financial lives. My recent work involved building and operating ML models that doubled marketing campaign conversion rates by generating 500M daily predictions.


At Bairesdev, I led the creation of ML models for consumer applications, specifically in prospect segmentation and rating, using advanced tools such as AWS and SparkML. This initiative not only served over a hundred clients but also demonstrated my capability in handling large-scale, consumer-focused solutions—a direct match for the responsibilities at Rocket Money.


My role also required scaling these models for improved speed and data capacity, where I defined the data architecture to optimize training processes, achieving a 10\% increase in performance metrics. This experience has prepared me to tackle similar challenges at Rocket Money, ensuring efficiency and effectiveness in model operations.


I am particularly drawn to Rocket Money due to its commitment to empowering individuals through innovative financial solutions. The opportunity to work at a company that prioritizes actionable insights for financial betterment aligns with my professional aspirations. Additionally, the focus on building self-sustaining engineering systems is an exciting challenge that I am eager to contribute to.


I believe my background in developing impactful machine learning solutions will be a valuable addition to Rocket Money. I am keen to bring my skills to your team and help drive the next generation of machine intelligence in the financial sector. I look forward to the possibility of discussing how I can contribute to your goals.

\vspace{1cm}
\setlength{\parskip}{0em}
\begin{flushright}
Sincerely,\\
Patricio Nicolas Massaro Rocca
\end{flushright}
\end{document}
