
\documentclass{article}
\usepackage[margin=1in]{geometry} % set the margins
\usepackage{graphicx} % package for including images
\usepackage{fancyhdr} % package for fancy header and footer
% all paragraphs should not be indented
\setlength\parindent{0pt}
% set the spacing between paragraphs
\setlength{\parskip}{1em}
\pagestyle{fancy}
\fancyhf{} % clear header/footer
\renewcommand{\headrulewidth}{0pt} % remove horizontal line in header

\begin{document}

\noindent Dear Hiring Manager,


I am a Lead Machine Learning Engineer with a robust background in developing and deploying advanced machine learning models. My recent work involved doubling marketing campaign conversion rates through sophisticated modeling techniques, aligning closely with the requirements of the Senior Machine Learning Engineer position at Reddit.


In my current role at Bairesdev, I spearheaded the development and implementation of industrial-level machine learning models for client segmentation and rating. This initiative, utilizing AWS and MLFlow, not only enhanced marketing efficiency but also served as a critical task in handling large-scale data, demonstrating my capability in tackling complex machine learning challenges and my drive for challenging work.


Another significant project involved designing and launching a deep neural network for natural language processing to optimize message classification. This reduced human workload by 37\% by incorporating advanced pooling and feature interactions. My approach not only streamlined operations but also showcased my affinity for deploying new model architectures, a key requirement for this role at Reddit.


I am particularly drawn to Reddit because of its commitment to fostering open and authentic conversations online, a value that resonates deeply with me. Additionally, the opportunity to work on predicting ads engagement rates to enhance marketplace efficiency is compelling due to its direct impact on business outcomes and its alignment with my past achievements.


I believe my experience in developing and deploying machine learning models, combined with my enthusiasm for Reddit's innovative environment, makes me a strong candidate for this position. I am eager to bring my expertise to your team and contribute to your mission of maximizing ad engagements and marketplace efficiency.

\vspace{1cm}
\setlength{\parskip}{0em}
\begin{flushright}
Sincerely,\\
Patricio Nicolas Massaro Rocca
\end{flushright}
\end{document}
