
\documentclass{article}
\usepackage[margin=1in]{geometry} % set the margins
\usepackage{graphicx} % package for including images
\usepackage{fancyhdr} % package for fancy header and footer
% all paragraphs should not be indented
\setlength\parindent{0pt}
% set the spacing between paragraphs
\setlength{\parskip}{1em}
\pagestyle{fancy}
\fancyhf{} % clear header/footer
\renewcommand{\headrulewidth}{0pt} % remove horizontal line in header

\begin{document}

\noindent Dear Hiring Manager,


As a Lead Machine Learning Engineer with considerable experience in the development and deployment of machine learning systems, I am eager to bring my capabilities to Stripe’s innovative risk engineering team. My tenure at Bairesdev has honed my skills in implementing technologies like AWS and Databricks to substantially enhance model accuracy and efficiency, much like the needs outlined for your role.


In my current position, I took the initiative to develop and launch machine learning models that significantly improved our client segmentation and ratings. Using AWS, Databricks, Airflow, MLFlow, and SparkML, these models now generate 500 million daily predictions, effectively doubling our marketing campaign conversion rates. These results underscore my capability to handle large datasets in a dynamic production environment, directly aligning with the challenges and responsibilities of this role at Stripe.


Another key requirement of your role is a proven track record in working within production systems to enhance operational efficiency and reliability. I've developed ML-based algorithms that have successfully reduced spam rates by 30\%, directly impacting platform security and reliability. This experience attests not only to my technical aptitude but also to my proactive approach in solving complex problems through innovative machine learning solutions.


Stripe’s commitment to increasing the GDP of the internet resonates deeply with my professional goals and personal interests in financial services technology. I am particularly impressed by your proactive approach to risk management and your dedication to creating robust, scalable financial infrastructure. This aligns with my passion for deploying technology to solve real-world problems, especially in environments that require both high reliability and innovative risk management strategies.


My experience and skills are well-matched to the needs of your team, and I am enthusiastic about the opportunity to contribute to your mission and further enhance Stripe’s impact on the financial industry. I look forward to the possibility of discussing how I can contribute to your continued success and innovation.

\vspace{1cm}
\setlength{\parskip}{0em}
\begin{flushright}
Sincerely,\\
Patricio Nicolas Massaro Rocca
\end{flushright}
\end{document}
