
\documentclass{article}
\usepackage[margin=1in]{geometry} % set the margins
\usepackage{graphicx} % package for including images
\usepackage{fancyhdr} % package for fancy header and footer
% all paragraphs should not be indented
\setlength\parindent{0pt}
% set the spacing between paragraphs
\setlength{\parskip}{1em}
\pagestyle{fancy}
\fancyhf{} % clear header/footer
\renewcommand{\headrulewidth}{0pt} % remove horizontal line in header

\begin{document}

\noindent Dear Hiring Manager,


I am a Lead Machine Learning Engineer with a robust background in deploying advanced machine learning models, particularly in natural language processing and deep learning. My recent project involved designing and implementing a deep learning model for natural language processing that reduced human workload by 37\%, aligning closely with the requirements of your Applied Scientist position at Grammarly.


Driven by curiosity and a passion for challenging work, I have successfully applied modern machine learning methods to solve complex problems in natural language processing. At Bairesdev, I spearheaded the development of a model that classifies inbound messages, significantly reducing manual intervention. This initiative not only optimized operational efficiency but also allowed for reallocation of resources to more strategic tasks, demonstrating my capability to enhance productivity through innovation.


My experience with deep learning extends to environmental monitoring, where I trained models using PyTorch for super-resolution applications. This work achieved a 20\% error reduction in land surface temperature estimations, crucial for effective wildfire management. My ability to lead these projects from conception through to successful implementation showcases my affinity for specific and impactful work, making me a valuable addition to Grammarly’s strategic research team.


Grammarly’s commitment to enhancing communication through advanced AI resonates deeply with my professional aspirations and personal values. The company’s emphasis on ethical AI development and remarkable innovation in writing assistance aligns with my goal to contribute to technology that makes a significant positive impact on everyday life. Additionally, Grammarly’s global presence and collaborative culture are incredibly appealing as they promise dynamic work environments and diverse perspectives.


I am eager to bring my specialized skills in machine learning and deep learning to Grammarly, particularly to contribute to your cutting-edge products and research initiatives. I look forward to the possibility of discussing how my background, skills, and enthusiasms align with the goals of your team.

\vspace{1cm}
\setlength{\parskip}{0em}
\begin{flushright}
Sincerely,\\
Patricio Nicolas Massaro Rocca
\end{flushright}
\end{document}
