
\documentclass[11pt,a4paper]{moderncv}
\moderncvtheme[green]{classic}                
\usepackage[T1]{fontenc}
\usepackage[utf8x]{inputenc}
\usepackage[italian]{babel}
\usepackage[scale=0.8]{geometry}
\recomputelengths                             

\fancyfoot{} 

\renewcommand*{\namefont}{\fontsize{25}{28}\mdseries\upshape}

\firstname{Patricio Nicolas}
\familyname{Massaro Rocca}

\mobile{+1-202-754-6052}                    
\email{patomassaro@gmail.com}                

\begin{document}
\maketitle
\vspace{-10mm}

\section{Work experience}

\cventry{2020 - 2024 }{Lead Data Scientist}{\href{https://www.bairesdev.com/}{Bairesdev}}{}{}{
\begin{itemize}
    \item Applied technical expertise in quantitative analysis and data presentation using AWS, Databricks, and MLFlow to develop and implement prospect segmentation strategies, significantly enhancing marketing conversion rates.
    \item Focused on developing hypotheses for early spam detection using machine learning methodologies and frameworks, successfully reducing spam rates by 30\%.
    \item Defined and tested data-driven strategies to enhance marketing efforts, using insights from AWS and SparkML to influence product roadmaps and double conversion rates.
    \item Designed and implemented a natural language processing deep learning model to classify inbound messages, reducing human workload by 37\%.
    \item Optimized data architecture to enhance ML models training, increasing performance metrics by 10\%.
    \item Utilized data analysis with Spark SQL and Tableau to shape marketing strategies, quantify new opportunities, and provide actionable insights to resonate with stakeholders and align with Atlassian's business objectives.
\end{itemize} 
}

\cventry{2023-2024}{Thesis working student}{\href{https://ororatech.com/}{Ororatech}}{}{}{  
\begin{itemize}
    \item Developed GANs in Pytorch for remote-sensing blind super-resolution, achieving a 20 \% error reduction in land surface temperature estimation with applications in wildfire management.
    \item Implemented a deep convolutional model for fine-scale georeferencing of thermal data products, improving accuracy in disaster monitoring applications.
    \item Published paper at IGARSS 2023 regarding multi-spectral remote sensing super-resolution.
\end{itemize} }

\cventry{ 2017 - 2020}{Business Intelligence Engineer}{\href{https://www.tenaris.com/en}{Tenaris}}{}{}{
 \begin{itemize}
     \item Led the architectural design and workflow development for migrating the entire organization to a centralized cloud-based PowerBI application for 30,000 contributors.
     \item Managed the population of the data warehouse using Synapse and Data Factory and designed the semantic layer using Azure Analysis Services, reducing costs by 17\%.
     \item Defined platform adoption KPIs and action plans for their improvement.
 \end{itemize}
 }

\cventry{ 2017 - 2018}{Research intern}{University of Buenos Aires}{}{}{ 
\begin{itemize}
     \item Two publications regarding the effects of piezoelectric devices in optoacoustic image reconstruction.
 \end{itemize}}

\cventry{2014 - 2017}{Systems Administrator}{Masstec S.R.L}{}{}{
    \begin{itemize}
        \item Administration of small businesses server, workstation, and networking systems.
    \end{itemize}
}

\cventry{2013- 2014}{Network administrator}{Education ministry, Buenos Aires}{}{}{
\begin{itemize}
    \item Coordinated the distribution of laptops and integrated ICT into educational practices in the context of the "Conectar Igualdad" program, enhancing digital literacy to over 250 students. 
\end{itemize}
}


\section{Education}
\cventry{2021-2023}{ Elite MSc Data Science}{\href{https://www.m-datascience.mathematik-informatik-statistik.uni-muenchen.de/index.html}{Ludwig-Maximilians-Universität}}{Munich}{Germany}{Thesis: Blind Super Resolution Applied to Thermal Remote Sensing Data Products}
\cventry{2020-2021}{ MSc Data Mining }{\href{http://datamining.dc.uba.ar/datamining/}{Universidad de Buenos Aires}}{}{Argentina}{}
\cventry{2010-2018}{Electronic Engineering}{\href{https://www.fi.uba.ar/}{Universidad de Buenos Aires}}{}{Argentina}{Thesis: Improvements in optoacoustic image reconstruction using deconvolution filters.} 


\section{Language}
\cvline{Spanish}{Native language.}
\cvline{English}{Bilingual proficiency.}
\cvline{German}{Professional working proficiency.}

\vspace{-3mm}

\end{document}
