
\documentclass{article}
\usepackage[margin=1in]{geometry} % set the margins
\usepackage{graphicx} % package for including images
\usepackage{fancyhdr} % package for fancy header and footer
% all paragraphs should not be indented
\setlength\parindent{0pt}
% set the spacing between paragraphs
\setlength{\parskip}{1em}
\pagestyle{fancy}
\fancyhf{} % clear header/footer
\renewcommand{\headrulewidth}{0pt} % remove horizontal line in header

\begin{document}

\noindent Dear Hiring Manager,


I am a Lead Machine Learning Engineer with a robust background in deploying sophisticated models to enhance user experiences. My recent project involved using AWS, Databricks, and MLFlow to double marketing campaign conversion rates by generating 500M daily predictions.


At my current role at Bairesdev, I've taken initiative by leading the development of early detection algorithms using machine learning, which reduced spam rates by 30\%. This project not only improved platform integrity but also fostered a collaborative environment among tech teams, aligning closely with your team's goals at Reddit to enhance personalization and recommendation systems.


Another significant part of my work involved managing the full software development cycle of a natural language processing model that reduced human workload by 37\%. This experience has equipped me with a comprehensive understanding of designing, developing, and deploying systems that significantly improve operational efficiency, which mirrors the responsibilities outlined for your Machine Learning Engineer position.


I am particularly drawn to Reddit because of its commitment to fostering open and authentic conversations online. The company's emphasis on impact, personal growth, and kindness resonates with my professional aspirations and personal values. Additionally, the opportunity to work remotely while contributing to a platform that reaches over 73 million daily users is incredibly appealing.


I believe my hands-on experience with machine learning and my proactive approach in tech environments make me a strong candidate for this role. I am eager to bring my skills to Reddit, where I can contribute to meaningful projects and further develop my abilities in a cutting-edge, supportive environment.

\vspace{1cm}
\setlength{\parskip}{0em}
\begin{flushright}
Sincerely,\\
Patricio Nicolas Massaro Rocca
\end{flushright}
\end{document}
