
\documentclass{article}
\usepackage[margin=1in]{geometry} % set the margins
\usepackage{graphicx} % package for including images
\usepackage{fancyhdr} % package for fancy header and footer
% all paragraphs should not be indented
\setlength\parindent{0pt}
% set the spacing between paragraphs
\setlength{\parskip}{1em}
\pagestyle{fancy}
\fancyhf{} % clear header/footer
\renewcommand{\headrulewidth}{0pt} % remove horizontal line in header

\begin{document}

\noindent Dear Hiring Manager,


I am a Lead Machine Learning Engineer eager to leverage my extensive experience in data-driven modeling and team leadership at Rocket Money. Having developed and implemented customer segmentation and conversion propensity models that doubled marketing campaign conversion rates, I am excited to bring similar transformative results to your team.


Leading projects from start to finish has been a cornerstone of my career. At Bairesdev, I spearheaded the Machine Learning department's first major initiatives, overseeing a team that delivered models generating 500 million daily predictions. This initiative not only doubled our conversion rates but also solidified my capability in managing high-stakes projects, ensuring that I can lead Rocket Money's initiatives towards success.


My experience with customer data extends to uncovering and exploiting relationships to enhance product personalization. By applying advanced data science techniques, I significantly improved engagement and conversion rates through tailored marketing strategies. This background makes me well-prepared to further Rocket Money's goals in creating personalized financial solutions that resonate with users.


Rocket Money's commitment to empowering individuals to optimize their financial lives deeply resonates with me. The mission to provide insights and services that save time and money aligns with my professional drive to create solutions that enhance efficiency and user satisfaction. Additionally, your leadership in the financial services industry is particularly appealing as it provides a platform for impactful, large-scale projects.


I am confident that my background in leading data-driven projects and my proactive approach to leveraging customer data for product enhancement will make a significant contribution to Rocket Money. I look forward to the possibility of discussing how my skills and experiences align with the goals of your team.

\vspace{1cm}
\setlength{\parskip}{0em}
\begin{flushright}
Sincerely,\\
Patricio Nicolas Massaro Rocca
\end{flushright}
\end{document}
