
\documentclass[11pt,a4paper]{moderncv}
\moderncvtheme[green]{classic}                % idem
\usepackage[T1]{fontenc}
\usepackage[utf8x]{inputenc}
\usepackage[italian]{babel}
\usepackage[scale=0.8]{geometry}
\recomputelengths                             

\fancyfoot{} 

\renewcommand*{\namefont}{\fontsize{25}{28}\mdseries\upshape}

\firstname{Patricio Nicolas}
\familyname{Massaro Rocca}

\mobile{+1-202-754-6052}                    
\email{patomassaro@gmail.com}                

\begin{document}
\maketitle
\vspace{-10mm}

\section{Work experience}

\cventry{2020 - 2024 }{Lead Machine Learning Engineer}{\href{https://www.bairesdev.com/}{Bairesdev}}{}{}{
\begin{itemize}
    \item Designed and deployed new models using SparkML, Tensorflow, and PyTorch for client segmentation, generating 500M daily predictions and significantly enhancing marketing campaign effectiveness.
    \item Iteratively improved verification and fraud detection models using ML-based algorithms, reducing fraud occurrences by 30% on the platform.
    \item Envisioned and developed new ML-based models for early fraud detection, achieving a 30% reduction in fraudulent activities.
    \item Proposed new feature ideas and designed real-time data pipelines, optimizing ML model training and enhancing performance metrics by 10%.
    \item Integrated new NLP signals into ML pipelines, derived new features, and built efficient workflows to classify inbound messages, reducing human workload by 37%.
    \item Ensured engineering outcomes met or exceeded standards in code quality, system design, and scalability during the architectural design and migration of a centralized cloud-based application for 30,000 users.
    \item Mentored and led a team of 3 engineers in the Machine Learning department, fostering technical growth and career development.
\end{itemize} 
}

\cventry{2023-2024}{Thesis working student}{\href{https://ororatech.com/}{Ororatech}}{}{}{  
\begin{itemize}
    \item Trained GANs in Pytorch for remote-sensing blind super-resolution, achieving a 20\% error reduction in land surface temperature estimation with applications in wildfire management.
    \item Implemented a deep convolutional model for fine-scale georeferencing of thermal data products, improving accuracy in disaster monitoring applications.
    \item Published paper at IGARSS 2023 regarding multi-spectral remote sensing super-resolution.
\end{itemize} }

\cventry{ 2017 - 2020}{Business Analytics Engineer}{\href{https://www.tenaris.com/en}{Tenaris}}{}{}{
 \begin{itemize}
     \item Led the architectural design and workflow development for migrating the entire organization to a centralized cloud-based PowerBI application for 30,000 contributors.
     \item Managed the population of the data warehouse using Synapse and Data Factory and designed the semantic layer using Azure Analysis Services, reducing costs by 17\%.
     \item Defined platform adoption KPIs and action plans for their improvement.
 \end{itemize}
 }

\cventry{ 2017 - 2018}{Research Intern}{University of Buenos Aires}{}{}{ 
\begin{itemize}
     \item Two publications regarding the effects of piezoelectric devices in optoacoustic image reconstruction.
 \end{itemize}}

\cventry{2014 - 2017}{Systems Administrator}{Masstec S.R.L}{}{}{
    \begin{itemize}
        \item Administration of small businesses server, workstation, and networking systems.
    \end{itemize}
}

\cventry{2013- 2014}{Network Administrator}{Education Ministry, Buenos Aires}{}{}{
\begin{itemize}
    \item Coordinated the distribution of laptops and integrated ICT into educational practices in the context of the "Conectar Igualdad" program, enhancing digital literacy to over 250 students. 
\end{itemize}
}


\section{Education}
\cventry{2021-2023}{Elite MSc Data Science}{\href{https://www.m-datascience.mathematik-informatik-statistik.uni-muenchen.de/index.html}{Ludwig-Maximilians-Universität}}{Munich}{Germany}{Thesis: Blind Super Resolution Applied to Thermal Remote Sensing Data Products}
\cventry{2020-2021}{MSc Data Mining }{\href{http://datamining.dc.uba.ar/datamining/}{Universidad de Buenos Aires}}{}{Argentina}{}
\cventry{2010-2018}{Electronic Engineering}{\href{https://www.fi.uba.ar/}{Universidad de Buenos Aires}}{}{Argentina}{Thesis: Improvements in optoacoustic image reconstruction using deconvolution filters.} 

\section{Language}
\cvline{Spanish}{Native language.}
\cvline{English}{Bilingual proficiency.}
\cvline{German}{Professional working proficiency.}

\vspace{-3mm}

\end{document}
