
\documentclass{article}
\usepackage[margin=1in]{geometry} % set the margins
\usepackage{graphicx} % package for including images
\usepackage{fancyhdr} % package for fancy header and footer
% all paragraphs should not be indented
\setlength\parindent{0pt}
% set the spacing between paragraphs
\setlength{\parskip}{1em}
\pagestyle{fancy}
\fancyhf{} % clear header/footer
\renewcommand{\headrulewidth}{0pt} % remove horizontal line in header

\begin{document}

\noindent Dear Hiring Manager,


I am a Lead Machine Learning Engineer with expertise in developing and deploying advanced machine learning solutions aimed at driving significant business results. In my role at Bairesdev, I successfully doubled the effectiveness of marketing campaigns by implementing segmentation and rating models using tools like SparkML and Tensorflow, aligning closely with your needs at Stripe for deploying new models to enhance payment intelligence.


My consistent focus on iterative model improvement has directly resulted in a 30\% reduction in fraudulent activities on our platform. This proactive approach resonates with Stripe’s goal to enhance the verification and fraud models, ensuring the security of millions of users. My ability to innovate and adapt ML solutions underlines my commitment to technical excellence and continuous learning, essential for leading in adversarial environments like payments and fraud detection.


In addition to my technical expertise, I have spearheaded the integration of new signals into ML pipelines, notably through NLP models that reduced human workload by 37\%. This ability to design and execute efficient workflows while incorporating new machine learning features could be instrumental in accelerating Stripe’s core payment flow and enhancing system scalability.


Stripe's mission to increase the GDP of the internet truly inspires me, as it aligns with my passion for leveraging technology to solve real-world challenges. The impact Stripe has made in scaling businesses and fostering financial progress demonstrates a commitment to innovation and excellence that I am eager to contribute to.


I am confident that my hands-on experience in machine learning and my strategic outlook will be an asset to your team. I am enthusiastic about the opportunity to bring my unique skills to Stripe and help shape the future of payment solutions globally.

\vspace{1cm}
\setlength{\parskip}{0em}
\begin{flushright}
Sincerely,\\
Patricio Nicolas Massaro Rocca
\end{flushright}
\end{document}
