
\documentclass{article}
\usepackage[margin=1in]{geometry} % set the margins
\usepackage{graphicx} % package for including images
\usepackage{fancyhdr} % package for fancy header and footer
% all paragraphs should not be indented
\setlength\parindent{0pt}
% set the spacing between paragraphs
\setlength{\parskip}{1em}
\pagestyle{fancy}
\fancyhf{} % clear header/footer
\renewcommand{\headrulewidth}{0pt} % remove horizontal line in header

\begin{document}

\noindent Dear Hiring Manager,


I am a Lead Machine Learning Engineer eager to advance my career by leveraging my extensive experience in machine learning and data architecture. My recent project involved designing and developing ML models for prospect segmentation and rating, from ideation to production deployment, using a variety of tools to double marketing campaign conversion rates.


At my current role in Bairesdev, I spearheaded the development of applied machine learning models that significantly enhanced marketing strategies by generating 500M daily predictions. This initiative not only doubled our conversion rates but also established a robust data-driven decision-making framework across the organization. My approach to machine learning is grounded in practical deployment and continuous improvement, making me an ideal candidate for designing and developing advanced models for Reddit's advertising platform.


Collaboration with data scientists and backend engineers has been a cornerstone of my professional journey. In a recent project, I utilized Spark SQL and Tableau to conduct in-depth data analyses that informed strategic decisions at the executive level. This experience highlights my capability to effectively collaborate within interdisciplinary teams to drive significant business outcomes, aligning perfectly with the collaborative environment at Reddit.


I am particularly drawn to Reddit because of its vibrant community and commitment to fostering open, authentic conversations. The opportunity to work on a platform that impacts millions daily is incredibly appealing to me, as it aligns with my passion for using technology to enhance user engagement and satisfaction.


I believe my background in deploying large-scale machine learning models and my proactive approach to collaboration and innovation will contribute effectively to Reddit's goals in ad measurement and system performance. I am keen to bring my skills to Reddit and help shape the future of advertising technology on one of the world's most influential platforms.

\vspace{1cm}
\setlength{\parskip}{0em}
\begin{flushright}
Sincerely,\\
Patricio Nicolas Massaro Rocca
\end{flushright}
\end{document}
