
\documentclass{article}
\usepackage[margin=1in]{geometry} % set the margins
\usepackage{graphicx} % package for including images
\usepackage{fancyhdr} % package for fancy header and footer
% all paragraphs should not be indented
\setlength\parindent{0pt}
% set the spacing between paragraphs
\setlength{\parskip}{1em}
\pagestyle{fancy}
\fancyhf{} % clear header/footer
\renewcommand{\headrulewidth}{0pt} % remove horizontal line in header

\begin{document}

\noindent Dear Hiring Manager,


I am a Lead Machine Learning Engineer with a robust background in developing advanced ML models and a passion for enhancing product capabilities through technology. My recent project involved designing and implementing a natural language processing model that reduced human workload by 37\%, directly aligning with your needs in NLP and predictive analytics.


In my current role at Bairesdev, I spearheaded the development of ML models for NLP to classify inbound messages, significantly reducing human workload. This initiative not only streamlined operations but also enhanced our predictive analytics capabilities, demonstrating my ability to lead projects that align with both technological advancement and business needs.


Collaboration with cross-functional teams has been a cornerstone of my approach, ensuring that ML and AI technologies are seamlessly integrated into business processes. For instance, I utilized Spark SQL and Tableau in data analysis to drive strategic decisions, which improved our understanding of business needs and pinpointed opportunities for technological applications. This experience prepares me to effectively collaborate with your product and engineering teams at Front.


I am particularly drawn to Front because of your innovative approach to customer service and the use of AI to enhance user engagement. Your commitment to reimagining help desks with real-time collaboration and advanced AI solutions resonates with my professional aspirations and my past experiences in pushing the envelope in ML applications.


I am eager to bring my expertise in ML, from conception to deployment, to Front, where I can contribute to pioneering new AI techniques and driving significant efficiency gains. I look forward to the possibility of discussing how my background, skills, and enthusiasms align with the goals of your team.

\vspace{1cm}
\setlength{\parskip}{0em}
\begin{flushright}
Sincerely,\\
Patricio Nicolas Massaro Rocca
\end{flushright}
\end{document}
