
\documentclass{article}
\usepackage[margin=1in]{geometry} % set the margins
\usepackage{graphicx} % package for including images
\usepackage{fancyhdr} % package for fancy header and footer
% all paragraphs should not be indented
\setlength\parindent{0pt}
% set the spacing between paragraphs
\setlength{\parskip}{1em}
\pagestyle{fancy}
\fancyhf{} % clear header/footer
\renewcommand{\headrulewidth}{0pt} % remove horizontal line in header

\begin{document}

\noindent Dear Hiring Manager,


I am a Lead Machine Learning Engineer with a robust background in data science, eager to leverage my expertise in a dynamic, growth-focused environment like Reddit. My recent work involved doubling marketing campaign conversion rates through advanced data modeling and analysis, a skill I am excited to bring to your team.


At Bairesdev, I worked closely with cross-functional teams to model and analyze data that significantly influenced marketing strategies, resulting in a 100\% increase in conversion rates. This experience has honed my ability to collaborate effectively with product, marketing, and business development teams, ensuring that data-driven insights lead to actionable business outcomes.


Additionally, I developed and utilized advanced dashboards in Tableau to analyze marketing spend, which played a crucial role in driving strategic decisions and optimizing return on investment. This aligns directly with your need for a Senior Data Scientist to develop tools for analyzing marketing spend performance. My approach not only enhances understanding but also drives efficiency in spending and resource allocation.


Reddit's commitment to fostering open and authentic conversations across a vast array of communities is truly inspiring. The platform's dedication to transparency and community engagement is something I deeply value. Moreover, Reddit's innovative approach to data utilization in understanding user behavior and improving user experience is particularly appealing to me, given my background and interests.


I am eager to bring my data science skills to Reddit, particularly to enhance the SMB Growth initiatives through strategic data analysis and insights. I look forward to the possibility of contributing to and growing with your esteemed team, and I am enthusiastic about the impact we can achieve together.

\vspace{1cm}
\setlength{\parskip}{0em}
\begin{flushright}
Sincerely,\\
Patricio Nicolas Massaro Rocca
\end{flushright}
\end{document}
