
\documentclass{article}
\usepackage[margin=1in]{geometry} % set the margins
\usepackage{graphicx} % package for including images
\usepackage{fancyhdr} % package for fancy header and footer
% all paragraphs should not be indented
\setlength\parindent{0pt}
% set the spacing between paragraphs
\setlength{\parskip}{1em}
\pagestyle{fancy}
\fancyhf{} % clear header/footer
\renewcommand{\headrulewidth}{0pt} % remove horizontal line in header

\begin{document}

\noindent Dear Hiring Manager,


I am a Lead Machine Learning Engineer with a robust background in data science, eager to leverage my skills in a dynamic environment like Reddit. My experience in developing and implementing machine learning models has directly contributed to doubling marketing campaign conversion rates by generating 500 million daily predictions.


At Bairesdev, I was deeply involved in all phases of product development, from ideation to post-launch monitoring. This role required a blend of technical expertise and strategic thinking, ensuring that our data-driven solutions were not only innovative but also aligned with broader business goals. My efforts led to significant improvements in campaign outcomes and client satisfaction.


My work also emphasized the importance of data integrity and operational efficiency. By conducting thorough data analyses and refining ETL processes, I enhanced decision-making and business tracking for top management. This experience has prepared me to handle the complex data systems at Reddit, ensuring that data quality and insightful reporting drive strategic decisions.


Reddit's commitment to fostering open and authentic conversations resonates with me. I admire how your platform manages to maintain a community-driven approach while scaling up technologically. This balance of growth and user-centric values is where I see my skills making a substantial impact.


I am eager to bring my analytical skills and strategic insights to Reddit, contributing to your team's success and continuing to grow both personally and professionally in this role. I look forward to the possibility of discussing how my background, skills, and enthusiasms align with the goals of Reddit.

\vspace{1cm}
\setlength{\parskip}{0em}
\begin{flushright}
Sincerely,\\
Patricio Nicolas Massaro Rocca
\end{flushright}
\end{document}
