
\documentclass{article}
\usepackage[margin=1in]{geometry} % set the margins
\usepackage{graphicx} % package for including images
\usepackage{fancyhdr} % package for fancy header and footer
% all paragraphs should not be indented
\setlength\parindent{0pt}
% set the spacing between paragraphs
\setlength{\parskip}{1em}
\pagestyle{fancy}
\fancyhf{} % clear header/footer
\renewcommand{\headrulewidth}{0pt} % remove horizontal line in header

\begin{document}

\noindent Dear Hiring Manager,


I am a Lead Machine Learning Engineer with four years of targeted experience, eager to leverage my expertise in complex problem-solving through machine learning. My recent project involved developing early detection algorithms, which successfully reduced spam rates by 30\%, showcasing my ability to address intricate data quality issues directly.


Taking initiative has always driven my professional endeavors. At Bairesdev, I crafted ML-based algorithms that directly tackled the pressing issue of platform spam. By applying intricate machine learning techniques, I not only mitigated spam by a significant margin but also enhanced the overall data quality, aligning perfectly with the responsibilities of the Applied Machine Learning Engineer role at Anomalo.


Driven by curiosity, I led a team to develop and deploy advanced machine learning features that doubled marketing campaign conversion rates by generating 500 million daily predictions. This initiative not only demonstrated my capability to enhance operational efficiency but also my commitment to leveraging technology to deliver tangible business outcomes. My experience in leading such high-impact projects will allow me to contribute effectively to Anomalo's goals.


Anomalo's commitment to 'Rational Optimism' and its innovative approach to data management solutions deeply resonate with my professional philosophy and aspirations. The transparent and values-driven culture promoted at Anomalo is particularly motivating, offering a vibrant environment for continuous learning and innovation.


I am convinced that my background in machine learning and my proactive approach to problem-solving make me a strong candidate for this position. I am keen to bring my skills to Anomalo to further enhance your suite of ML tools and contribute to innovative data quality solutions. I look forward to the possibility of discussing this exciting opportunity with your team.

\vspace{1cm}
\setlength{\parskip}{0em}
\begin{flushright}
Sincerely,\\
Patricio Nicolas Massaro Rocca
\end{flushright}
\end{document}
