\documentclass[11pt,a4paper]{moderncv}
\moderncvtheme[green]{classic}                % idem
\usepackage[T1]{fontenc}
\usepackage[utf8x]{inputenc}
\usepackage[italian]{babel}
\usepackage[scale=0.8]{geometry}
\recomputelengths                             

\fancyfoot{} 


\renewcommand*{\namefont}{\fontsize{25}{28}\mdseries\upshape}

\firstname{Patricio Nicolas}
\familyname{Massaro Rocca}

\address{District of Columbia, USA}{}    % optional, remove the line if not wanted
\mobile{+1-202-754-6052}                    
\email{patomassaro@gmail.com}                
% \photo[105pt]{cv.png}      


\begin{document}
\maketitle
\vspace{-10mm}

%Section
% \section{Personal information}
% \cvcomputer{Birth date}{\small 1992/02/27\normalsize}{Nationality:}{\small Argentina \normalsize}

\vspace{-4mm}

% \section{Profile}

% \cvline{} {Holding a Master's degree in Data Science from LMU Munich, complemented by a background in electronic engineering, I bring 5 years of experience designing and implementing end-to-end machine learning pipelines aligned to business needs. I am eager to leverage my expertise in a role that challenges me to contribute to solutions and products that would improve people's lives. 
% }

\section{Work experience}

\cventry{2020 - 2024 }{Lead Machine Learning engineer}{\href{https://www.bairesdev.com/}{Bairesdev}}{}{}{
\begin{itemize}
    \item First hire in the Machine Learning department of the company's growth acceleration service, leading a team of 3 people.
    \item Train and implement prospect segmentation and rating models for over a hundred clients using AWS, Databricks, Airflow, MLFlow, and SparkML, generating 500M daily predictions and doubling marketing campaign conversion rates.
    \item Develop ML-based anomaly detection algorithms, reducing the platform spam rate by 30\%.
    \item Design and implement a natural language processing deep learning model to classify inbound messages, reducing human workload by 37\%.
    \item Definition of the data architecture to optimize ML models training, increasing performance metrics by 10\%.
    \item Conduct data analysis with Spark SQL and Tableau to drive strategic decision-making processes among top management.
\end{itemize} 
}

\cventry{2023-2024}{Thesis working student}{\href{https://ororatech.com/}{\href{https://ororatech.com/}{Ororatech}}}{}{}{  \begin{itemize}
    \item Train GANs in Pytorch for remote-sensing blind super-resolution, achieving a 20 \% error reduction in land surface temperature estimation with applications in wildfire management.
    \item Implement a deep convolutional model for fine-scale georeferencing of thermal data products, improving accuracy in disaster monitoring applications.
    \item Publish paper at IGARSS 2023 regarding multi-spectral remote sensing super-resolution.
\end{itemize} }

\cventry{ 2017 - 2020}{Business analytics
 engineer}{\href{https://www.tenaris.com/en}{Tenaris}}{}{}{
 \begin{itemize}
     \item Led the architectural design and workflow development for migrating the entire organization to a centralized cloud-based PowerBI application for 30,000 contributors.
     \item Manage the population of the data warehouse using Synapse and Data Factory and design the semantic layer using Azure Analysis Services, reducing costs by 17\%.
     \item Definition of platform adoption KPIs and action plans for their improvement.
 \end{itemize}
 }

 \cventry{ 2017 - 2018}{Research intern}{University of Buenos Aires}{}{}{ \begin{itemize}
     \item Two publications regarding the effects of piezoelectric devices in optoacoustic image reconstruction.
 \end{itemize}}

 \vspace{0.2cm}
\cventry{2014 - 2017}{Systems Administrator}{Masstec S.R.L}{}{}{
    \begin{itemize}
        \item Administration of small businesses server, workstation, and networking systems.
    \end{itemize}
}
\vspace{0.2cm}
\cventry{2013- 2014}{Network administrator}{Education ministry, Buenos Aires}{}{}{
\begin{itemize}
    \item Coordinate the distribution of laptops and integrate ICT into educational practices in the context of the "Conectar Igualdad" program, enhancing digital literacy  to over 250 students. 
\end{itemize}
}


\section{Education}
\cventry{2021-2023}{ Elite MSc Data Science}{\href{https://www.m-datascience.mathematik-informatik-statistik.uni-muenchen.de/index.html}{Ludwig-Maximilians-Universität}}{Munich}{Germany}{Thesis: Blind Super Resolution Applied to Thermal Remote Sensing Data Products}
\cventry{2020-2021}{ MSc Data Mining }{\href{http://datamining.dc.uba.ar/datamining/}{Universidad de Buenos Aires}}{}{Argentina}{}
\cventry{2010-2018}{Electronic Engineering}{\href{https://www.fi.uba.ar/}{Universidad de Buenos Aires}}{}{Argentina}{Thesis: Improvements in optoacoustic image reconstruction using deconvolution filters.} 



% The project consisted in the development and implementation of an analytical model for the broadband device, a reconstruction algorithm and a deconvolution filter to minimize the distortion introduced by the sensor.  





% \section{Academic experience}

% \cventry{2019}{DAAD}{Study trip scholarship}{Design and development of a 3-D bioprinter}{}{ I was awarded with a scholarship from the DAAD, for a 2-week study trip, visiting several universities in Baden-Württemberg and Bavaria. I participated in seminars, lab immersions and debates regarding the state of the art of biofabrication and additive manufacturing. The conclusions of this work were reflected in a book under the ISBN 978-987-778-959-1.}

%Section

%Section



\section{Language}
\cvline{Spanish}{Native language.}
\cvline{English}{Bilingual proficiency.}
\cvline{German}{Professional working proficiency.}

\vspace{-3mm}





\end{document}